### 2021-10-18 test/lambdapure/compile/bench/speedup-rgn.tex
show that programs look different, but performance is the same

\begin{axis}[
legend cell align={left},
legend columns=100,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, at={(1,1.3)}, draw=none},
tick align=outside,
tick pos=left,
x grid style={white!69.0196078431373!black},
xmin=-0.82, xmax=6.22,
xtick style={color=black},
xtick={0,1,2,3,4,5,6},
xticklabel style={rotate=15.0},
xticklabels={binarytrees-int,binarytrees,const\_fold,deriv,filter,rbmap\_checkpoint,unionfind},
y grid style={white!69.0196078431373!black},
ylabel style={rotate=-90.0},
ylabel={Runtimes},
ymin=0, ymax=1.491,
ytick style={color=black}
]
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.1,1);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0}
\addlegendentry{λpure simplifier}

\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.9,1.01);
\draw[draw=none,fill=color0] (axis cs:1.7,0) rectangle (axis cs:1.9,1.3);
\draw[draw=none,fill=color0] (axis cs:2.7,0) rectangle (axis cs:2.9,0.78);
\draw[draw=none,fill=color0] (axis cs:3.7,0) rectangle (axis cs:3.9,0.97);
\draw[draw=none,fill=color0] (axis cs:4.7,0) rectangle (axis cs:4.9,1.15);
\draw[draw=none,fill=color0] (axis cs:5.7,0) rectangle (axis cs:5.9,0.85);
\draw[draw=none,fill=color1] (axis cs:-0.5,0) rectangle (axis cs:-0.3,1);
\addlegendimage{ybar,ybar legend,draw=none,fill=color1}
\addlegendentry{rgn simplifier}

\draw[draw=none,fill=color1] (axis cs:0.5,0) rectangle (axis cs:0.7,1);
\draw[draw=none,fill=color1] (axis cs:1.5,0) rectangle (axis cs:1.7,1.42);
\draw[draw=none,fill=color1] (axis cs:2.5,0) rectangle (axis cs:2.7,0.96);
\draw[draw=none,fill=color1] (axis cs:3.5,0) rectangle (axis cs:3.7,1.12);
\draw[draw=none,fill=color1] (axis cs:4.5,0) rectangle (axis cs:4.7,1.01);
\draw[draw=none,fill=color1] (axis cs:5.5,0) rectangle (axis cs:5.7,1);
\draw (axis cs:-0.3,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:0.7,1.01) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:1.7,1.3) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.3};
\draw (axis cs:2.7,0.78) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.78};
\draw (axis cs:3.7,0.97) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.97};
\draw (axis cs:4.7,1.15) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.15};
\draw (axis cs:5.7,0.85) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.85};
\draw (axis cs:-0.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:0.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:1.5,1.42) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.42};
\draw (axis cs:2.5,0.96) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.96};
\draw (axis cs:3.5,1.12) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.12};
\draw (axis cs:4.5,1.01) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:5.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\end{axis}

>>>>

\begin{axis}[
legend cell align={left},
legend columns=100,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, at={(1,1.3)}, draw=none},
tick align=outside,
tick pos=left,
x grid style={white!69.0196078431373!black},
xmin=-0.82, xmax=6.22,
xtick style={color=black},
xtick={0,1,2,3,4,5,6},
xticklabel style={rotate=15.0},
xticklabels={binarytrees-int,binarytrees,const\_fold,deriv,filter,rbmap\_checkpoint,unionfind},
y grid style={white!69.0196078431373!black},
ylabel style={rotate=-90.0},
ylabel={Runtimes},
ymin=0, ymax=1.1865,
ytick style={color=black}
]
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.1,1);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0}
\addlegendentry{λpure simplifier}

\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.9,1);
\draw[draw=none,fill=color0] (axis cs:1.7,0) rectangle (axis cs:1.9,1.01);
\draw[draw=none,fill=color0] (axis cs:2.7,0) rectangle (axis cs:2.9,1);
\draw[draw=none,fill=color0] (axis cs:3.7,0) rectangle (axis cs:3.9,1.03);
\draw[draw=none,fill=color0] (axis cs:4.7,0) rectangle (axis cs:4.9,1.13);
\draw[draw=none,fill=color0] (axis cs:5.7,0) rectangle (axis cs:5.9,0.86);
\draw[draw=none,fill=color1] (axis cs:-0.5,0) rectangle (axis cs:-0.3,1);
\addlegendimage{ybar,ybar legend,draw=none,fill=color1}
\addlegendentry{rgn simplifier}

\draw[draw=none,fill=color1] (axis cs:0.5,0) rectangle (axis cs:0.7,1);
\draw[draw=none,fill=color1] (axis cs:1.5,0) rectangle (axis cs:1.7,1);
\draw[draw=none,fill=color1] (axis cs:2.5,0) rectangle (axis cs:2.7,1);
\draw[draw=none,fill=color1] (axis cs:3.5,0) rectangle (axis cs:3.7,1.01);
\draw[draw=none,fill=color1] (axis cs:4.5,0) rectangle (axis cs:4.7,0.98);
\draw[draw=none,fill=color1] (axis cs:5.5,0) rectangle (axis cs:5.7,0.99);
\draw (axis cs:-0.3,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:0.7,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:1.7,1.01) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:2.7,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:3.7,1.03) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.03};
\draw (axis cs:4.7,1.13) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.13};
\draw (axis cs:5.7,0.86) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.86};
\draw (axis cs:-0.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:0.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:1.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:2.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:3.5,1.01) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:4.5,0.98) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.98};
\draw (axis cs:5.5,0.99) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.99};
\end{axis}
